Is it time for an NBA expansion?

### 2024-04-12 paper/paper.qmd
Added Toc
Saved Clean data

---
title: "Is it time for an NBA expansion?"
subtitle: "My subtitle if needed"
author: 
  - Yan Mezhiborsky
thanks: "Code and data are available at: ."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

```{r}

@@

```{r}

#combining data into one table
combined_data <- data.frame()

@@

  # Combine with the main data frame
  combined_data <- bind_rows(combined_data, yearly_data)
}

# creating table for league average
league_average_data <- combined_data %>% 
  filter(Team == "League Average")

>>>>

---
title: "Is it time for an NBA expansion?"
subtitle: "My subtitle if needed"
author: 
  - Yan Mezhiborsky
thanks: "Code and data are available at: ."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

@@

```{r}
#| include: false
#| warning: false
#| message: false
#| 
#combining data into one table
combined_data <- data.frame()

@@

  # Combine with the main data frame
  combined_data <- bind_rows(combined_data, yearly_data)
}
#Remove Less important columns
full_nba_data <- combined_data %>% select(-"G", -"MP", -"2P", -"2PA", -"2P%")

# creating table for league average
nba_data <- full_nba_data %>% 
  filter(Team == "League Average")

write.csv(nba_data, "../data/clean_data/nba_data.csv", row.names = FALSE)
write.csv(full_nba_data, "../data/clean_data/full_nba_data.csv", row.names = FALSE)
```
